---
title: "Arifu Hackathon: Challenge3 Modelling
author: "Jane Kathambi"
date: "4 May 2019"
output: 
  html_document:
    keep_md: yes
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
# Introduction


# Load the required libraries
```{r message=FALSE}
library(gmodels)
library(tidyverse)
library(caret)
library(caTools)
library(gridExtra)
library(readr)
library(lubridate)
library(stringr)
library(DT)

seed=2010
```

# Load the data
```{r message=FALSE}
credit_data<-read_csv('data/credit data.csv')
```

# IDA

## Introduce the data
```{r}
introduce(credit_data)
```

## Plot the data introduction
```{r}
plot_intro(credit_data)
```

## Look at the columns that have missing values
```{r}
miss_var_summary(credit_data)
```

## Plot the missing data
```{r}
plot_missing(credit_data)
```


## Look at the internal structure
```{r}
glimpse(credit_data)
```

## Drop zero var variables
```{r}
# Obtain zero and near zero variance variables
NZV<- nearZeroVar(credit_data, saveMetrics = TRUE)

# view
NZV

# set row names into a column, name it variable_name
NZV<-NZV%>%
  tibble::rownames_to_column(var = 'variable_name')

# confirm
NZV
```


```{r}
# Extract the names of zero variance features
variables_to_drop<-NZV%>%
  filter(zeroVar== TRUE )%>%
  select(variable_name)%>%
  pull()

variables_to_drop
```

There are npo zero var variables


## Distribution of categorical variables
```{r}
plot_bar(credit_data)
```

## Distribution of numerical variables
```{r}
plot_histogram(credit_data%>%select(-observation_id)
               )
```

## Response variable coding
```{r}
CrossTable(credit_data$default)
```

The imbalance in the classes is noted for modeling as more information is available to classify the paid_in_full class, which may allow some models to result in good accuracy when predicting the paid_in_full class, but poor accuracy when predicting the default class while having good overall accuracy. For this reason I will use the AUC metric for model evaluation.

Let us coarse response variable to factor:
```{r}
credit_data$default<-ifelse(credit_data$default==2, 'default','paid_in_full' )

credit_data$default<-as.factor(credit_data$default)
```

```{r}
# Call CrossTable() on loan_status_360
prop.table(table(credit_data$default))
```

